Scalar and Representative Observables, and Their Associated Statistical Model, for Polarimetric SAR Data

### 2014-03-03 paper_dev/article.tex
ks confidence level

Similarly, Fig. \ref{fig:verify_det_ratio_model_3D} explores the $d=3$ case for the same data, same model parameters.
Again, although the histogram is much tighter, the match is visually obvious in all cases.
This qualitative observation is further supported by high significance level (or p-value) of the standard Kolmogorov-Smirnov goodness-of-fit test between curves, noted under each graph.
While a good p-value does not ensure automatic acceptance of the model,
  consistently high p-value lend evidence the proposed model has excellent confidence\cite{Kolmogoroff_1941_AMS_461}.

>>>>

Similarly, Fig. \ref{fig:verify_det_ratio_model_3D} explores the $d=3$ case for the same data, same model parameters.
Again, although the histogram is much tighter, the match is visually obvious in all cases.
This qualitative observation is further supported by high significance level (or p-value) of the standard Kolmogorov-Smirnov goodness-of-fit test between curves, noted under each graph.
While a good p-value does not ensure automatic acceptance of the model,
  consistently high p-values lend high level of confidence to the proposed model\cite{Kolmogoroff_1941_AMS_461}.
